Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-16 article.rnw
Fix the rounding for AICc values in the manuscript.
For some reason, the precision to print them to wasn't specified.
Fix a hard-coded number in the results, and reword the sentence around it.
The sentence said "just over 7", so it had to be reworded if the
number wasn't going to be hard-coded.

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\icnum[1]{\num{#1}} %For information criteria.
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
\Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
Despite it being just over $7$ {\ic} units from the most parsimonious model, the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.

>>>>

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\icnum[1]{\num[round-mode=places,round-precision=2]{#1}} %For information criteria.
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

The ``best'' model, as indicated by {\ic}, was not the best with any surety; its Akaike weight indicated a probability of only \probnum{\Sexpr{max(brute_data$statistics[[ic_weight]])}} that it was the best.
\Cref{fig:best-model} shows the groupings and alpha values of this ``best'' model.
The ungrouped model had an {\ic} just \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]] - min(brute_data$statistics[[ic]])}} units from the most parsimonious model, but the total Akaike weight assigned to models more parsimonious than the ungrouped model was \probnum{\Sexpr{sum(brute_data$statistics[[ic_weight]][brute_data$statistics[[ic]] < brute_data$fully_separated_statistics[[ic]]])}}; this is the probability that some grouped model was more parsimonious than the ungrouped model.
